Exploring Transfer Learning with Fluorescence Cell Image

### 2019-11-27 paper/paper.tex
fixed problems with .bib

The input of our model consists of 224x224x3 sized arrays, they first go through a batch normalization layer\cite{ioffe2015batch}. This helps
us normalize the input to the pre-trained model on our specific dataset, allowing us 
to feed the raw data in without much pre-processing.

The ResNet50V2 model is conveniently structured as distinct residual blocks.
For our experiments, we picked the outputs of 4 different residual blocks, evenly spaced between each other, in the model
as our final feature map. The output of the chosen hidden layers is a large number of feature maps. Due to limitations of our compute resources, we chose not to directly flatten the feature maps and connect it to a dense prediction
layer due to the number of feature maps ResNet50V2 outputs and thus the number of parameters that would need. We chose to reduce the number of feature maps from the output by first passing it through a 1x1 convolution layer\cite{szegedy2014going} with 
relu activation. This allows us to reduce the number of final feature maps in an efficient way, significantly reducing the number of parameters and training time. 
We then flatten the feature maps using global average pooling\cite{Lin2013NetworkIN}, and then connect to a 
fully connected dense layer for prediction.

The dataset we are tackling is a multi-label classification problem, therefore use sigmoid activation
in the prediction layer as each image can belong in multiple classes. We use binary cross-entropy as the loss function. 
\begin{equation}
    L(Y, \hat{Y}) = \sum_i^n y_i\log{(\hat{y}_i)}
\end{equation}
Where $Y$ is the "multi hot" representation of our label, $y_i$
is the value at each $i^{th}$ position in the label.  We assume that for every value in the output vector $\hat{y_i}$ is the probability
that an image is in class $i$, where each $\hat{y}_i$ is indenpendent of other class probabilities because 
each $x$ can belong to multiple classes at the same time.

@@

\subsection{Human Protein Dataset}
\begin{figure}[ht]
    \centering
    \begin{subfigure}[b]{0.8\linewidth}
      \includegraphics[width=\linewidth]{paper/figures/accuray.png}
    \end{subfigure}

    \begin{subfigure}[b]{0.8\linewidth}
      \includegraphics[width=\linewidth]{paper/figures/loss.png}
    \end{subfigure}
    \caption{Example images from the Human Protein dataset}
  \end{figure}

>>>>

The input of our model consists of 224x224x3 sized arrays, they first go through a batch normalization layer\cite{ioffe2015batch}. This helps
us normalize the input to the pre-trained model on our specific dataset, allowing us 
to feed the raw data in without much pre-processing.
\\
\\
The ResNet50V2 model is conveniently structured as distinct residual blocks.
For our experiments, we picked the outputs of 4 different residual blocks, evenly spaced between each other, in the model
as our final feature map. The output of the chosen hidden layers is a large number of feature maps. Due to limitations of our compute resources, we chose not to directly flatten the feature maps and connect it to a dense prediction
layer due to the number of feature maps ResNet50V2 outputs and thus the number of parameters that would need. We chose to reduce the number of feature maps from the output by first passing it through a 1x1 convolution layer\cite{szegedy2014going} with 
relu activation. This allows us to reduce the number of final feature maps in an efficient way, significantly reducing the number of parameters and training time. 
We then flatten the feature maps using global average pooling\cite{Lin2013NetworkIN}, and then connect to a 
fully connected dense layer for prediction. 
\\
\\
The dataset we are tackling is a multi-label classification problem, therefore use sigmoid activation
in the prediction layer as each image can belong in multiple classes. We use binary cross-entropy as the loss function. 
\begin{equation}
    L(Y, \hat{Y}) = \sum_i^n y_i\log{(\hat{y}_i)}
\end{equation}
Where $Y$ is the "multi hot" representation of our label, $y_i$
is the value at each $i^{th}$ position in the label.  We assume that for every value in the output vector $\hat{y_i}$ is the probability
that an image is in class $i$, where each $\hat{y}_i$ is indenpendent of other class probabilities because 
each $x$ can belong to multiple classes at the same time.

@@

\subsection{Human Protein Dataset}
\begin{figure}[ht]
    \centering
    \begin{subfigure}[b]{0.8\linewidth}
      \includegraphics[width=\linewidth]{accuray.png}
    \end{subfigure}

    \begin{subfigure}[b]{0.8\linewidth}
      \includegraphics[width=\linewidth]{loss.png}
    \end{subfigure}
    \caption{Training loss and accuracy of each model}
  \end{figure}
